Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
Potential

>>>>

To compute initial conditions for the stream model, we fit an orbit to the
observed properties of the stream in a fixed model for the gravitational
potential of the Milky Way.
We use a three-component potential model to represent the Galaxy, consisting of
a Miyamoto-Nagai disk (\citealt{Miyamoto:1975}), a Hernqust bulge
(\citealt{Hernquist:1990}), and a spherical Navarro-Frenk-White dark matter halo
(\citealt{Navarro:1996}).
We set the disk scale-length parameters to closely match the disk model found in
\citet{Bovy:2015}, and other parameters are set to reproduce an approximately
flat rotation curve between $5 < R < 15~\kpc$ with a circular velocity at the
solar circle, $v_{\textrm{circ}, \odot} \approx 230~\kms$.

To initialize the model stream generation, we \todo{...}

Stream properties computed from resulting model stream are plotted in \figurename~\ref{fig:track-and-model} as \todo{XX}.
